Plots for Latent Hawkes Paper

### 2020-07-13 output_scripts/Paper_Plots.Rmd

<!-- # Figure 7: Pearson residual matrices -->

<!-- Here is where I need to be a bit more careful about using the correct fits. -->
<!-- Currently using all from Jing's saved output. -->

<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->

<!-- ```{r} -->
<!-- current_cohort <- 1 -->

<!-- m1_residual_matrix_lst <- list() -->
<!-- m2_residual_matrix_lst <- list() -->
<!-- m3_residual_matrix_lst <- list() -->
<!-- mmhp_residual_matrix_lst <- list() -->

<!--   print(current_cohort) -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
<!--   unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
<!--     summarize(count=n(), -->
<!--               observe=list(observe.id), -->
<!--               observe.length=list(observe.time), -->
<!--               no.events=list(no.events)) -->
<!--   unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->

<!--   # M1 -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cohort_hp_stan_result_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!--   model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0), -->
<!--                          eta_1=mean(sim_cohort_hp$eta_1), -->
<!--                          eta_2=mean(sim_cohort_hp$eta_2), -->
<!--                          eta_3=mean(sim_cohort_hp$eta_3), -->
<!--                          beta=mean(sim_cohort_hp$beta), -->
<!--                          f=apply(sim_cohort_hp$f,2,mean)) -->
<!--   model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0, -->
<!--                                                   nrow=mice_number,ncol=mice_number), -->
<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
<!--                                                                                       model1_par_est$eta_1, -->
<!--                                                                                       model1_par_est$eta_2, -->
<!--                                                                                       model1_par_est$eta_3), -->
<!--                                                     model1_par_est$f), -->
<!--                             beta_matrix=matrix(model1_par_est$beta, -->
<!--                                                nrow=mice_number,ncol=mice_number)) -->
<!--   m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->

<!--   for(i in 1:mice_number){ -->
<!--     for(j in 1:mice_number){ -->
<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--       if(length(pair)>0&(i!=j)){ -->
<!--         par_est <- lapply(model1_par_matrix, function(x) x[i,j]) -->
<!--         names(par_est) <- c("lambda0","alpha","beta") -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         all_residual <- 0 -->
<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
<!--           cur_win <- current_window_vec[cur] -->
<!--           current_event_time <- return_df[return_df$initiator==i& -->
<!--                                             return_df$recipient==j& -->
<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--           current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient==j& -->
<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
<!--                                                                   events=current_event_time, -->
<!--                                                                   termination = current_obs_time) -->
<!--         } -->
<!--         m1_residual_matrix[i,j] <- all_residual -->
<!--       } -->
<!--     } -->
<!--   } -->

<!--   # M2 -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!--   model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean), -->
<!--                          zeta=apply(sim_cohort_dchp$zeta,2,mean), -->
<!--                          eta_1=mean(sim_cohort_dchp$eta_1), -->
<!--                          eta_2=mean(sim_cohort_dchp$eta_2), -->
<!--                          eta_3=mean(sim_cohort_dchp$eta_3), -->
<!--                          beta=mean(sim_cohort_dchp$beta), -->
<!--                          f=apply(sim_cohort_dchp$f,2,mean)) -->
<!--   model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+ -->
<!--                               rep(1,mice_number)%*%t(model2_par_est$zeta), -->
<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
<!--                                                                                       model2_par_est$eta_1, -->
<!--                                                                                       model2_par_est$eta_2, -->
<!--                                                                                       model2_par_est$eta_3), -->
<!--                                                     model2_par_est$f), -->
<!--                             beta_matrix=matrix(model2_par_est$beta, -->
<!--                                                nrow=mice_number,ncol=mice_number)) -->
<!--   m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->

<!--   for(i in 1:mice_number){ -->
<!--     for(j in 1:mice_number){ -->
<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--       if(length(pair)>0&(i!=j)){ -->
<!--         par_est <- lapply(model2_par_matrix, function(x) x[i,j]) -->
<!--         names(par_est) <- c("lambda0","alpha","beta") -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         all_residual <- 0 -->
<!--         for(cur in c(1:length(current_window_vec))){  -->
<!--           cur_win <- current_window_vec[cur] -->
<!--           current_event_time <- return_df[return_df$initiator==i& -->
<!--                                             return_df$recipient==j& -->
<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--           current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient==j& -->
<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
<!--                                                                   events=current_event_time, -->
<!--                                                                   termination = current_obs_time) -->
<!--         } -->
<!--         m2_residual_matrix[i,j] <- all_residual -->
<!--       } -->
<!--     } -->
<!--   } -->

<!-- ```   -->

<!-- This is too large to load at the moment again. Can do this on the cluster. -->

<!-- ```{r, eval=FALSE}   -->
<!--   # M3 -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->
<!--   model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0), -->
<!--                          lambda1=mean(sim_cohort_mmhp$lambda1), -->
<!--                          eta_1=mean(sim_cohort_mmhp$eta_1), -->
<!--                          eta_2=mean(sim_cohort_mmhp$eta_2), -->
<!--                          eta_3=mean(sim_cohort_mmhp$eta_3), -->
<!--                          beta=mean(sim_cohort_mmhp$beta), -->
<!--                          f=apply(sim_cohort_mmhp$f,2,mean)) -->
<!--   model3_par_matrix <- list(lambda0_matrix=matrix(model3_par_est$lambda0, -->
<!--                                                   nrow=mice_number,ncol=mice_number), -->
<!--                             lambda1_matrix=matrix(model3_par_est$lambda1, -->
<!--                                                   nrow=mice_number,ncol=mice_number), -->
<!--                             alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y, -->
<!--                                                                                       model3_par_est$eta_1, -->
<!--                                                                                       model3_par_est$eta_2), -->
<!--                                                     model3_par_est$f), -->
<!--                             beta_matrix=matrix(model3_par_est$beta, -->
<!--                                                nrow=mice_number,ncol=mice_number), -->
<!--                             q1_matrix=formMatrix(function(x,y) model3_fn$q1.fun(x,y,model3_par_est$eta_3), -->
<!--                                                  model3_par_est$f), -->
<!--                             q2_matrix=formMatrix(function(x,y) model3_fn$q0.fun(x,y,model3_par_est$eta_3), -->
<!--                                                  model3_par_est$f)) -->
<!--   m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
<!--   no_segments <- 5000 # changed from 5000 -->
<!--   window_pr <- c() -->
<!--   for(i in 1:mice_number){ -->
<!--     print(i) -->
<!--     for(j in 1:mice_number){ -->
<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--       if(length(pair)>0&(i!=j)){ -->
<!--         par_est <- lapply(model3_par_matrix, function(x) x[i,j]) -->
<!--         names(par_est) <- c("lambda0","lambda1","alpha","beta","q1","q2") -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         all_residual <- 0 -->
<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
<!--           cur_win <- current_window_vec[cur] -->
<!--           current_event_time <- return_df[return_df$initiator==i& -->
<!--                                             return_df$recipient==j& -->
<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--           current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient==j& -->
<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
<!--           time_segment <- seq(0,current_obs_time,length.out=no_segments) -->
<!--           latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean) -->
<!--           latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)  -->
<!--           est.intensity <- mmhpIntensityNumeric(params=par_est, -->
<!--                                                 t=current_event_time, -->
<!--                                                 time.vec=time_segment, -->
<!--                                                 latent.vec=latent_mean) -->
<!--           est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time, -->
<!--                                                         latent_z=latent_event) -->
<!--           all_residual <- all_residual + sum(1/sqrt(est.intensity.events))- -->
<!--             sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]) -->
<!--           # print(sum(1/sqrt(est.intensity.events))- -->
<!--           #         sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])) -->
<!--           # print(summary(latent_mean)) -->
<!--           # window_pr <- c(window_pr,sum(1/sqrt(est.intensity.events))- -->
<!--           #                  sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])) -->
<!--         } -->
<!--         m3_residual_matrix[i,j] <- all_residual -->
<!--       } -->
<!--     } -->
<!--   } -->

<!-- ```   -->
<!-- These are in part 1 of the thesis folder on Google Drive. -->

<!-- ```{r, eval=FALSE} -->
<!-- ind_mmhp_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part1/real_data/" -->
<!--   # Independent MMHP -->
<!--   load(paste(ind_mmhp_data_path, cohort_names[current_cohort],  -->
<!--              "/sep_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep='')) -->
<!--   load(paste(ind_mmhp_data_path,cohort_names[current_cohort], -->
<!--              "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->

<!--   mmhp_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
<!--   for(i in 1:mice_number){ -->
<!--     print(i) -->
<!--     for(j in 1:mice_number){ -->
<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--       if(length(pair)>0&(i!=j)){ -->
<!--         par_est <- list(lambda0=mean(sim_mmhp_sep$lambda0[,pair]), -->
<!--                         lambda1=mean(sim_mmhp_sep$lambda1[,pair]), -->
<!--                         alpha=mean(sim_mmhp_sep$alpha[,pair]), -->
<!--                         beta=mean(sim_mmhp_sep$beta[,pair]), -->
<!--                         q1=mean(sim_mmhp_sep$q1[,pair]), -->
<!--                         q2=mean(sim_mmhp_sep$q2[,pair])) -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         all_residual <- 0 -->
<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
<!--           cur_win <- current_window_vec[cur] -->
<!--           current_event_time <- return_df[return_df$initiator==i& -->
<!--                                             return_df$recipient==j& -->
<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--           current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient==j& -->
<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
<!--           time_segment <- seq(0,current_obs_time,length.out=no_segments) -->
<!--           latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean) -->
<!--           latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)  -->
<!--           est.intensity <- mmhpIntensityNumeric(params=par_est, -->
<!--                                                 t=current_event_time, -->
<!--                                                 time.vec=time_segment, -->
<!--                                                 latent.vec=latent_mean) -->
<!--           est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time, -->
<!--                                                         latent_z=latent_event) -->
<!--           all_residual <- all_residual + sum(1/sqrt(est.intensity.events))- -->
<!--             sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]) -->
<!--         } -->
<!--         mmhp_residual_matrix[i,j] <- all_residual -->
<!--       } -->
<!--     } -->
<!--   } -->
<!--   m1_residual_matrix_lst[[current_cohort]] <- m1_residual_matrix -->
<!--   m2_residual_matrix_lst[[current_cohort]] <- m2_residual_matrix -->
<!--   m3_residual_matrix_lst[[current_cohort]] <- m3_residual_matrix -->
<!--   mmhp_residual_matrix_lst[[current_cohort]] <- mmhp_residual_matrix -->

<!-- save(m1_residual_matrix_lst, m2_residual_matrix_lst, m3_residual_matrix_lst, mmhp_residual_matrix_lst, -->
<!--      file = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData") -->
<!-- beepr::beep() -->
<!-- ``` -->
<!-- These would need to be rerun correctly and saved. -->
<!-- For now using an *old* version. -->

<!-- ```{r} -->
<!-- load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData") -->
<!-- png(paste(plot_path,"real_residual_matrix_one_cohort.png",sep=""),width = 800,height = 400) -->
<!-- matrix_lst_plot <- list( -->
<!--                         mmhp_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
<!--                                                                    expert_rank_10[[current_cohort]]], -->
<!--                         m1_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
<!--                                                                  expert_rank_10[[current_cohort]]], -->
<!--                         m2_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
<!--                                                                  expert_rank_10[[current_cohort]]], -->
<!--                         m3_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
<!--                                                                  expert_rank_10[[current_cohort]]])  -->
<!-- myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2, -->
<!--                   xLabels=expert_rank_10[[current_cohort]], -->
<!--                   yLabels=rev(expert_rank_10[[current_cohort]]), -->
<!--                   min=-63,max=63,axis_cex=2,title_cex = 1.8, -->
<!--                   colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.95), -->
<!--                   title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"),  -->
<!--                   #title_lst = list("I-MMHP"), -->
<!--                   col_axis=c(-60,-30,0,30,60), out.title="", fake_matrix=FALSE, -->
<!--                   matrix.mar=c(2.5,2.5,2.5,2)) -->
<!-- dev.off() -->
<!-- ``` -->
<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->

<!-- # Figure 8 -->

<!-- ## Figure 8a: Frobenius norm of interaction predictions, single cohort -->

>>>>

```{r fig-6b-overall-rank-correlation}
load("../output/weighted_rank_data.RData")
#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = viridis::viridis(4)) + 
        ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2

# Figure 7: Pearson residual matrices

Here is where I need to be a bit more careful about using the correct fits.
Currently using all from Jing's saved output.

In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.

```{r fig-7-prMatrix-Cohort1}
current_cohort <- 1

m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                   "/chp_pr_matrix_",cohort_names[current_cohort],
                   ".RDS",sep=''))

m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                     "/dchp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                     "/immhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

```
<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->

# Figure 8

## Figure 8a: Frobenius norm of interaction predictions, single cohort

```{r fig-8a-frob-norm-cohort1}
load("../output/plot_N_predict.RData")
current_cohort <- 1

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- ggplot(temp_plot_df, aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 50)
p3
```

## Figure 8b: Same plot aggregated for all cohorts

```{r fig-8b-frob-norm-all-cohorts}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarize(avg=mean(norm), n= n(), sd=sd(norm))

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)

#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) 
p4
```

# Figure 9

## Figure 9a: Predicted Spearman rank for single cohort

```{r fig-9a-spearman-rank-cohort1}
load("../output/plot_rank_predict.RData")
current_cohort <- 1
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") +
  ylim(0, 1)
p5
```

## Figure 9b: Predicted Spearman rank for all cohorts

```{r fig-9b-spearman-rank-all-cohorts}
load("../output/plot_rank_predict.RData")
temp_plot_df <- all_cohort_rank_df %>% 
  group_by(day, method) %>% 
  summarize(avg=mean(spearman), n= n(), sd=sd(spearman))

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)

# png(paste(plot_path,"real_predict_rank_all_cohort.png",sep=""),width=600,height=300)
p6 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                position=position_dodge(0.2)) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") + 
  coord_cartesian(ylim=c(0,1)) + 
  guides(color=guide_legend(title="Model")) 
p6
```

# Figure 10

## Figure 10a

```{r construct data for plot, results='hide',message=FALSE}
library(PlayerRatings)
load(paste(data_path,cohort_names[current_cohort],
           "/predict_simulation_",cohort_names[current_cohort],
           ".RData",sep=''))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]],
                        cut_off = 1)

df <- full_data[[cohort_names[current_cohort]]]
df <- df[df$Actor!="Start"&df$Actor!="End",]
df1 <- expandrows(df)
df1 <- df1[order(df1$Timestamp),] #ensure in date order
df1$event <- 1:nrow(df1)
glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE] #need event, actor, recipient, score
gl <- my_glicko(glick.df, history=TRUE, cval=2)

# ------------------- period
training_end <- nrow(df[df$day<=18,])
testing_end <- 1076
newx <- c(training_end:testing_end)

# ----------------- set pars for plot
my_col <- c("black", "grey", "orange", "red")
col_vec <- colorRampPalette(my_col)(mice_number)
ltypes_vec <- rep(1,mice_number) #c(1,2,3,1,2,3,1,2,3,1,2,3)
history_width <- 3
sim_width <- 0.3
shade_vec <- makeTransparent(col_vec,0.2)
less_shade_vec <- makeTransparent(col_vec,0.7)

# ---------------- simulation mean and sd
sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
for(s in 1:100){
  print(s)
  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(predict.sim = m3_predict_sim[5:8,s],
                                                       history.df = glick.df[1:training_end,])
  history_matrix <- temp_gl$history[,,1]

  if(testing_end>ncol(temp_gl$history[,,1])){
    history_matrix <- cbind(history_matrix,
                            t(matrix(rep(history_matrix[,ncol(history_matrix)],testing_end-ncol(temp_gl$history[,,1])),
                                     nrow=testing_end-ncol(temp_gl$history[,,1]),byrow=TRUE)))
  }else{
    history_matrix <- temp_gl[,1:testing_end]
  }
  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
}
```

```{r fig-10a-glicko-rating}
par(mar=c(3,5,3,1))
plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
     cex.axis=2, cex.lab=2)
for(m in c(1:mice_number)){
  #history
  lines(gl$history[m,1:training_end,1],
        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])

  #simulation
  cur_end <- testing_end
  mean_vec <- apply(sim_gl_array[m,,],1,function(x) mean(na.omit(x)))
  sd_vec <- apply(sim_gl_array[m,,],1,function(x) sd(na.omit(x)))
  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),col = shade_vec[m], border = NA)
  #polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
  lines(c(rep(NA,training_end),mean_vec),
        cex=0.6, col=col_vec[m],lwd=1,lty=2)
}

# annotate the days
for(d in c(19:21)){
  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
}
mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
```

```{r remove some objects, include=FALSE}
rm(m3_predict_sim)
rm(m2_predict_sim)
rm(m1_predict_sim)
rm(mmhp_predict_sim)
rm(fit_agg_rank)
rm(fit_cohort_hp)
rm(fit_cohort_dchp)
rm(fit_cohort_mmhp)

# also removing stan fits as they can cause issues in the next chunk

## Fig 10b

```{r process for state separation cohort1,eval=FALSE}
# only run this once and save the results
# this doesn't need to be rerun ever, even if the stan fits change
load(paste(data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],
             ".RData",sep=''))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("day","observe.id","observe.time")])

## 5.  find how many 1s for each pair
print(".......state separation plot........")
total_event_array <- array(0,dim=c(mice_number,mice_number,max(return_df$observe.id)))
active_event_array <- array(0,dim=c(mice_number,mice_number,max(return_df$observe.id)))

for(i in 1:mice_number){
  for(j in c(1:mice_number)[-i]){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0){
      current_window_vec <- unique_pairs_df$observe[[pair]]
      for(cur_win in current_window_vec){
        row_indicator <- return_df$initiator==i&return_df$recipient==j&return_df$observe.id==cur_win
        total_event_array[i,j,cur_win] <- length(return_df[row_indicator,"event.times"][[1]])
        active_event_array[i,j,cur_win] <- sum(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)
      }
    }
  }
}

utility_state_day <- array(0,dim=c(21,mice_number,mice_number))
social_state_day <- array(0,dim=c(21,mice_number,mice_number))
for(cur_day in c(1:21)){
  cur_wins <- which(unique_observe_win$day==cur_day)
  utility_state_day[cur_day,,] <- apply(active_event_array[,,cur_wins],c(1,2),sum)
  social_state_day[cur_day,,] <- apply(total_event_array[,,cur_wins],c(1,2),sum)-utility_state_day[cur_day,,]
}

## utility dsnl
fit_dsnl_active <- stan("../lib/dsnl_poisson.stan",
                         data=list(day=21,
                                   Gt=utility_state_day,
                                   c=1,
                                   sigma=0.5),
                         iter=1000, chains=4, control=list(adapt_delta=0.99))
print(fit_dsnl_active,pars=c("x"))
sim_dsnl_active <- rstan::extract(fit_dsnl_active)

## social dsnl
fit_dsnl_inactive <- stan("../lib/dsnl_poisson.stan",
                           data=list(day=21,
                                     Gt=social_state_day,
                                     c=1,
                                     sigma=1),
                           iter=1000, chains=4, control=list(adapt_delta=0.99))
print(fit_dsnl_inactive,pars=c("x"))
sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)

save(sim_dsnl_active, fit_dsnl_active, utility_state_day,
     sim_dsnl_inactive, fit_dsnl_inactive, social_state_day,
     file = paste(data_path,cohort_names[current_cohort],
                  "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
                  ".RData",sep=''))
rm(interpolation_array_list)
rm(state_array_list)
rm(termination_state_list)
rm(initial_state_list)
```

```{r process data for plot 10b}
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);
